Automated Topic Naming

### 2012-01-18 ese/ese.tex
intro comments from migod

Researchers have employed a variety of techniques to extract underlying
topics that relate to software development artifacts.  Typically, these
techniques use semi-unsupervised machine-learning algorithms to suggest
candidate word-lists.  However, word-lists are
difficult to 
interpret in the absence of meaningful summary labels.  Current topic modeling 
techniques assume manual labelling and do not use domain-specific knowledge
to improve, contextualize, or describe results for the developers.  
We propose a solution: \emph{automated labelled topic extraction}.
  Topics are extracted 
using  Latent Dirichlet Allocation (LDA) from commit-log comments recovered
from source control systems. % such as CVS and BitKeeper.  
These topics are given labels from a generalizable
cross-project taxonomy, consisting of non-functional
requirements. Our approach was evaluated with experiments and case studies
on three large-scale Relational Database Management System (RDBMS) projects: MySQL, PostgreSQL and MaxDB.  
The case studies
show that labelled topic extraction can produce appropriate,
context-sensitive labels relevant to these projects, which provides fresh
insight into their evolving software development activities.
%160 words
\keywords{ Software maintenance \and Repository mining \and Latent Dirichlet allocation \and Topic models}

@@

\section{Introduction}
A key problem for practicing software maintainers is gaining an
understanding of \emph{why} a system has evolved the way it has \cite{Mockus00}. 
This is different from \emph{how} a system has evolved. 
% NE this phrase confuses me: "because the change of behaviour itself is the \emph{how}.
Looking back on streams of artifacts scattered across different
repositories, inferring what activities were performed, when, and for
what reasons, is hard without expert advice from the developers
involved. 
%new stuff
% edit this. awkward
In this work we provide a method of automatically labelling  development topics extracted from commit logs.

Concrete applications of topics and \emph{labelled topic extraction}, which this paper introduces,
range from project dashboards to annotating software artifacts such as revisions and bug reports with
NFR-related tags.
Project dashboards~\cite{dashboard} are typically employed by managers and are used to
provide quick summaries of the effort put into a software project. In this case, 
labelled topic extraction would allow managers to track effort
related to NFR topics, such as \emph{portability}.
These techniques also allow for the annotation of commit comments
 and other software artifacts with NFRs. 
This would enable querying of bug reports and artifacts by relevant NFRs. 
For instance a manager can confirm if their developers were
focused on \emph{usability} by looking for
 \emph{usability}-relevant revisions and bug reports.

Topic modeling (such as Latent Dirichlet Allocation ~\cite{Blei2003}) is a machine learning technique that creates
multinomial distributions of words extracted from a text corpus. 
This technique infers the hidden structure of a corpus using posterior
inference: the probability of the hidden structure given the data. 
Topic models are useful in software maintenance because they summarize
the key concepts in a corpus, such as source code, commit comments, or
mailing-list messages, by identifying statistically co-occurring words. 
Among other uses, it can quickly give developers an overview of where significant
activity has occurred, and gives managers or maintainers a sense of
project history.

%migod
While machine learning techniques can automatically identify clumps of
commonly recurring terms, devising an appropriate summary label for
each clump/topic is harder.  
A given topic extracted from a set of commit logs might consist of the following terms: \emph{ ``listener change remove add fire''}. 
This topic might reasonably be labelled as
\emph{``event handling''} by a developer who understands the domain well,
despite the fact that this label does not appear in the word list itself.  
Current approaches to topic labelling rely on manual intervention by
human experts, and also are limited to project-specific topic labels.  
In this paper, we introduce \emph{labelled topic extraction}, an
approach to topic labelling that labels topics automatically with
labels that are project independent.

@@

This paper makes the following contributions: 
\begin{itemize}
\item introduces the concept of labelled topic extraction, using a non-functional requirements (NFR) taxonomy for our labels;

%\item evaluates an unsupervised method of automated topic labelling (word-lists);
%%\item Our unsupervised method can be applied to projects without training;
%%\item 
%evaluates a supervised method of automatically labelling topics with a single NFR (machine learning);
%%\item 
%evaluates a supervised method of labelling topics with multiple NFRs
%(multi-label machine learning);

\item evaluates three kinds of automatic topic labelling methods:
  semi-unsupervised labelling  of topics (word-lists), supervised labelling of
  topics with a single NFR (machine learning), 
  and supervised labelling of topics with multiple NFRs (multi-label
  machine learning);

%  of automated topic labelling (word-lists);
%\item Our unsupervised method can be applied to projects without training;
%\item 
%evaluates a supervised method of automatically labelling topics with a single NFR (machine learning);
%\item 
%evaluates a supervised method of labelling topics with multiple NFRs (multi-label machine learning);

\item examines how NFRs correlate with the work of individual developers;
\item provides a method of cross-project analysis via topic labelling; and
 applies these techniques to visualize NFRs over time, and to analyze maintenance activities.

@@

This work extends our previous work~\cite{msr2011}, published at the
Working Conference on Mining Software Repositories 2011
(MSR'2011). The major extensions in this paper are as follows:
\begin{itemize}
	\item We added more machine learning results and another case-study: PostgreSQL. 
	\item We used two authors to each annotate the same PostgreSQL topics in order to compare
them. 
	\item We used this new case-study to test inter-rater reliability, described in Section \ref{sec:inter-rater}. 
	\item We conducted an analysis of PostgreSQL authors and their association with NFRs and
topics (Section \ref{sec:developers}).
\end{itemize}

@@

Cleland-Huang and her colleagues have investigated mining requirements
documents for non-functional requirements (NFR) (software
qualities)~\cite{Cleland-Huang2006}.  
%Their approach is similar to
%ours, as they mine keywords from NFR catalogues.  They differ from our approach because
%they mine requirements documents whereas we mine revisions.
One approach they tried was similar to this one, with keywords mined from NFR catalogues found in Chung et al.~\cite{corollary99}. 
Their approach resulted in a recall of $80\%$ with precision of $57\%$ for the \emph{security} NFR, but could not find a reliable source of keywords for other NFRs. 
Instead, they developed a supervised classifier by using human experts to identify an NFR training set. 
Our research is different because we use a more comprehensive set of terms based on a taxonomy that is an integral part of our framework.
Another difference is that we make cross-project comparisons instead of focusing
on a single project.
They relied on relatively well-structured requirements documents instead of version control histories that we use.
The objective of Cleland-Huang's study was to identify new NFRs for system development, 
yet our objective was to recover those latent NFRs from commit-log messages of the project.

@@

\subsection{Inter-rater reliability}

To determine inter-rater reliability two of the authors---Ernst and Hindle---each annotated the PostgreSQL topics,
and then evaluated each other's annotations.

>>>>

Researchers have employed a variety of techniques to extract underlying
topics that relate to software development artifacts.  Typically, these
techniques use semi-unsupervised machine-learning algorithms to suggest
candidate word-lists.  However, word-lists are
difficult to 
interpret in the absence of meaningful summary labels.  Current topic modeling 
techniques assume manual labelling and do not use domain-specific knowledge
to improve, contextualize, or describe results for the developers.  
We propose a solution: \emph{automated labelled topic extraction}.
  Topics are extracted 
using  Latent Dirichlet Allocation (LDA) from commit-log comments recovered
from source control systems. % such as CVS and BitKeeper.  
These topics are given labels from a generalizable
cross-project taxonomy, consisting of non-functional
requirements. Our approach was evaluated with experiments and case studies
on three large-scale Relational Database Management System (RDBMS) projects: MySQL, PostgreSQL and MaxDB.  
The case studies
show that labelled topic extraction can produce appropriate,
context-sensitive labels that are relevant to these projects, and provide fresh
insight into their evolving software development activities.
%160 words
\keywords{ Software maintenance \and Repository mining \and Latent Dirichlet allocation \and Topic models}

@@

\section{Introduction}
A key problem for practicing software maintainers is gaining an
understanding of \emph{why} a system has evolved the way it has \cite{Mockus00}. 
This is different from \emph{how} a system has evolved. 
% NE this phrase confuses me: "because the change of behaviour itself is the \emph{how}.
Looking back on streams of artifacts scattered across different
repositories, inferring what activities were performed, when, and for
what reasons, is hard without expert advice from the developers
involved. 
%new stuff
% edit this. awkward
In this work we provide a method of automatically labelling  development topics extracted from commit logs called \emph{labelled topic extraction}.

Concrete applications of \emph{labelled topic extraction} include the annotation of development artifacts with NFR-related tags and the creation of project dashboards.  Annotating software development artifacts with NFR-related tags would allow developers to create detailed directed queries of different artifact kinds that concern the same NFR; for example, a developer could browse the recent history of performance-related bug reports and code check-ins. Project dashboards distill detailed information about a software system into a simpler and more abstract view that summarizes key aspects of the development effort \cite{dashboard}; labelled topic extraction would allow managers to track effort related to specific NFR topics, such as \emph{usability} or \emph{portability}.

Topic modeling (such as Latent Dirichlet Allocation ~\cite{Blei2003}) is a machine learning technique that creates
multinomial distributions of words extracted from a text corpus. 
This technique infers the hidden structure of a corpus using posterior
inference: the probability of the hidden structure given the data. 
Topic models are useful in software maintenance because they summarize
the key concepts in a corpus -- such as source code, commit comments, or
mailing-list messages -- by identifying words that commonly occur together. 
Among other uses, topic modelling can quickly give developers an overview of where significant
activity has occurred, and provide managers or maintainers an enhanced understanding of the project's 
history.

%migod
While machine learning techniques can automatically identify clumps of
commonly recurring terms, devising an appropriate summary label for
each clump/topic is harder.  
A given topic extracted from a set of commit logs might consist of the following terms: \emph{ ``listener change remove add fire''}. 
This topic might reasonably be labelled as
\emph{``event handling''} by a developer who understands the domain well,
despite the fact that this label does not appear in the word list itself.  
Current approaches to topic labelling rely on manual intervention by
human experts, and also are limited to project-specific topic labels.  
In this paper, we introduce \emph{labelled topic extraction}, an
approach that automatically suggests project-independent labels for topics.

@@

This paper makes the following contributions: 
\begin{itemize}
\item We introduce the concept of labelled topic extraction, using a taxonomy of non-functional requirements (NFR) for our labels; 
\item We evaluate three kinds of automatic topic labelling methods:
  semi-unsupervised labelling  of topics (word-lists), supervised labelling of
  topics with a single NFR (machine learning), 
  and supervised labelling of topics with multiple NFRs (multi-label
  machine learning);
\item We examine how NFRs correlate with the work of individual developers;
\item We provide a method of cross-project analysis via topic labelling, and
we apply these techniques to visualize NFRs over time, and to analyze maintenance activities.

@@

This work extends our previous work~\cite{msr2011}. The major extensions in this paper are as follows:
\begin{itemize}
	%\item We added new results on developer activities.
	\item We conducted another case-study on PostgreSQL. 
	\item We used two authors to each annotate the same PostgreSQL topics in order to compare
these annotations. 
	\item We used this new case-study to test inter-rater reliability, described in Section \ref{sec:inter-rater}. 
	\item We conducted an analysis of PostgreSQL authors and their association with NFRs and
topics (Section \ref{sec:developers}).
\end{itemize}

@@

Cleland-Huang and her colleagues have investigated mining requirements
documents for non-functional requirements (NFR) (software
qualities)~\cite{Cleland-Huang2006}.  
%Their approach is similar to
%ours, as they mine keywords from NFR catalogues.  They differ from our approach because
%they mine requirements documents whereas we mine revisions.
One approach they tried was similar to this one, with keywords mined from NFR catalogues found in Chung et al.~\cite{corollary99}. 
Their approach resulted in a recall of $80\%$ with precision of $57\%$ for the \emph{security} NFR, but could not find a reliable source of keywords for other NFRs. 
Instead, they developed a supervised classifier by using human experts to identify an NFR training set. 
Our research is different because we use a more comprehensive set of terms based on a taxonomy that is an integral part of our framework.
Another difference is that we make cross-project comparisons instead of focusing
on a single project.
They relied on relatively well-structured requirements documents instead of version control histories that we use.
The objective of Cleland-Huang's study was to identify new NFRs for system development, 
while our objective was to recover those latent NFRs from commit-log messages of the project.

@@

\subsection{Inter-rater reliability}
\label{sec:inter-rater}
To determine inter-rater reliability two of the authors---Ernst and Hindle---each annotated the PostgreSQL topics,
and then evaluated each other's annotations.
